Workflow and Software Documentation

### 2013-07-13 Workflow.Rnw
Added example of finding fraction of unconverged resample fits.
Added a demonstration of specifying the country order for a graph.

\item
Other examples:
<<>>=
head( loadAllResampleData(model="sf", factor="K"), n=3 )
head( loadAllResampleData(model="linex", energyType = "Q"), n=3 )
head( loadAllResampleData(model="cese", energyType = "Q"), n=3 )
@
\end{enumerate}
\end{enumerate}

@@

<<>>=
standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q"), 
                     aes(a_0, c_t) ) +
  labs(title="Model = linex; energy=Q", x=expression(a[0]), y=expression(c[t]))
@

>>>>

\item
Other examples:
<<>>=
head( loadAllResampleData(model="sf", factor="K"), n=3 )
head( loadAllResampleData(model="linex", energyType = "Q"), n=3 )
head( loadAllResampleData(model="cese", energyType = "Q"), n=3 )
@
\end{enumerate}

\item To find the fraction of resample models that do not converge, say
<<>>=
fracUnconvergedResampleFitsAll()
@

\end{enumerate}

@@

<<>>=
standardScatterPlot( loadAllResampleData(model="linex", energyType = "Q", 
                                         countryAbbrevsOrder=c("US", "UK", "JP", "CN", 
                                                               "ZA", "TZ", "SA", "IR", "ZM")), 
                     aes(a_0, c_t) ) +
  labs(title="Model = linex; energy=Q", x=expression(a[0]), y=expression(c[t]))
@
